
\subsection{Purpose}
This document has the purpose of guiding the developer in the realization process of the \textbf{CLup} software, an innovative application to manage queues digitally.\newline
Due to the Coronavirus emergency grocery shopping needs to follow strict rules: supermarkets need to restrict access to their stores which typically results in long lines forming outside.The goal of this project is to develop an easy-to-use application that allows store managers to regulate the influx of people and that saves people from having to crowd outside of stores.\newline
The application releases a number that gives the position in the queue and gives information about the time when that number is called, in this way the user is able to arrive to the supermarket and enter immediately. \newline
Clup allows also the user to book a slot to enter the supermarket indicating the expected time to shop, or alternatively the application itself can infer it.\newline
Finally the application can suggest different slots to visit the store, based on stores crowdedness, and slots in alternative stores, based on the day/hour preferences of the user.   

\subsubsection{Goals}

\begin{table} [H]
\rowcolors{1}{Goldenrod}{white}
\begin{tabular}{l|l}
	G1 & \pbox{13cm}{Anybody is guaranteed possibility to make shopping at any supermarket in reasonable time (def. reasonable)}\\
	G2 & Users can get to know the least crowded time slots\\
	G3 & Fair users can make a reservation to enter in a supermarket\\
	G4 & Stores can easily monitor fluxes\\
	G5 & Only authorized users can access\\
	G6 & Crowds are dramatically reduced outside supermarket stores\\
    G7 & \pbox{13cm}{CLup should not decrease customer affluence beyond a reasonable level w.r.t. to normal (→ define reasonable)}\\
    G8 & Same shopping capabilities guaranteed to offline users\\
    G9 & \pbox{13cm}{Find the best (less crowded, soonest available) alternative among local supermarket stores (of same franchise only?)}\\
    G10 & Supermarkets do not overcrowd
\end{tabular}
\caption{Goal list}
\label{tab:GoalList}
\end{table}

\subsection{Scope}


\subsubsection{World Phenomena}

\begin{table}[H]
\rowcolors{1}{Goldenrod}{white}
\begin{tabular}{l|l}
	WP1 & User leaves home to go to the supermarket\\\hline
	WP2 & Users crowd outside the store\\\hline
    WP3 & User arrives at the supermarket\\\hline
    WP4 & User enters the supermarket \\\hline
	WP5 & User does the grocery shopping \\\hline
	WP6 & User exits the supermarket\\\hline
	WP7 & Supermarkets restrict accesses in stores\\\hline %do we need this?
	WP8 & User buys products of a non booked category\\\hline %is this a world or shared phenomena?
\end{tabular}
\caption{World phenomena list}
\label{tab:WorldPhen}
\end{table}

\subsubsection{Shared Phenomena}
\begin{table} [H]
\rowcolors{1}{Goldenrod}{white}
\begin{tabular}{l|l}
	SP1 & User lines up using the application \\
	SP2 & User makes a reservation \\
	SP3 & User keeps track of how line evolves \\
	SP4 & User validates the entrance with a QR code \\
	SP5 & User receives suggestion for less crowded time slots \\
	SP6 & User receives suggestion for less crowded stores \\
	SP7 & CLup assigns a time slot \\
	SP8 & CLup signals max number of customers inside the store has been reached \\
	SP9 & CLup signals customer for improper behavior \\
	SP10 & Offline customer interacts with physical totem \\
	SP11 & User confirms booking \\
	SP12 & User confirms ticket reservation \\
	
\end{tabular}
\caption{Shared phenomena list}
\label{tab:SharedPhen}
\end{table}
\subsection{Definitions, Acronyms, Abbreviations}

\subsubsection{Definitions\label{subsub:definitions}}
\begin{itemize}
\item \textbf{Check-in procedure}: the process of getting inside the store. It starts from when the user approaches the entrance, includes the QR ticket scan and ends as soon as the turnstile is passed.
\item \textbf{Reserve entrance}: the process of booking a future entrance (starting from the day next to the current one)
\item \textbf{Malicious user}: someone committed for any reason to CLup malfunction and/or unavailability, shopping disservices.
\item \textbf{Quick ticket}: the actual ticket granting access to the stores. We call it \guillemotleft quick\guillemotright \space to emphasize the difference between booking and lining up.
\item \textbf{Totem}: a desktop based PC with advanced input functionalities (touchscreen), with external hard shell protection, stand mount, (optional) integrated printer.
\item \textbf{Big screen}: a huge screen panel to be located outside the store, in visible placement, used for announcements to offline customers.
\item \textbf{CLup core system\label{core_functionality}}: CLup innermost back-end functionality providing queueing control, access to already enqueued users, access control, big screens operativeness                                                                                                                                                                                                   \end{itemize}


\subsubsection{Acronyms}
\begin{itemize}
\item \textbf{EWT}: Expected Waiting Time
\item \textbf{ASAP}: As Soon As Possible
\item \textbf{WRT}: With Respect To
\end{itemize}

\subsubsection{Abbreviations}


\subsection{Revision History}
\begin{itemize}
	\item \textbf{v1.0}: First version of the document
	\item \textbf{v1.1}: Section 4 revision
	\item \textbf{v1.2}: Sections 3.3, 3.4 revision
	\item \textbf{v1.3}: Section 4.2 revision, sequence diagrams upscaling
	\item \textbf{v1.4}: Front page addition, minor syntax revisions
	
\end{itemize}


\subsection{Reference Documents}
This documents has been designed by taking the \textbf{ISO/IEC/IEEE 29148} as primary reference.\cite{STANDARD}\newline


\noindent Other documents of sources have been cited along the way whenever needed.

\subsection{Document Structure}
\paragraph{Chapter 1}
gives an introduction about the purpose of the document and the development of the application, with its corresponding specifications such as the definitions, acronyms, abbreviation,
revision history of the document and the references.\newline
The structure of the document is also analyzed.

\paragraph{Chapter 2}
contains the overall description of the project. In the product perspective are included the state-charts of the main application functions, the overall Class Diagram and a brief description for it. \newline 
In user characteristic application target is further analyzed, as well as the functionalities of the application. \newline
Finally, the taken domain assumptions are exposed.


\paragraph{Chapter 3}
exposes interface requirements including: user, hardware, software and communication interfaces. This section contains the core of the document, specifications over
functional and non-functional requirements. \newline
Functional requirements are paired with a list of use cases and the corresponding sequence diagrams, plus some scenarios. Non-functional requirements include performance, design and security constraints.


\paragraph{Chapter 4}
includes the alloy code and the automated worlds generated, together with model testing results.

\paragraph{Chapter 5}
 delineates the effort spent in creating each section of this Document, per author.

\paragraph{Chapter 6}
 is an overall list of the main source references.

%what you write here is a comment that is not shown in the final text
